
---
title: RMarkdown Primer
author : Emilie Hamel
output : 
    html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, fig.align = 'center', eval = TRUE)
```

# Example RMarkdown document 
This is an interactive document written in *markdown*. As you can see it is easy to include: 

  1. Ordered lists 
  2. *Italics* 
  3. **Bold type** 
  4. Links to [Documentation](https://rmarkdown.rstudio.com/) 
    
## This is heading two 
Perhaps this introduces the visualisation below. 

So if we type the letter r then hit Shift + Tab on the keyboard, it creates a chunk but also has placeholders for the label and any options.

## R code chunk

```{r ajouter-un-label-ici}
8+192
```


# Data Display

```{r load-data}
library(ggplot2)
data(diamonds)
```

```{r table1}
head(diamonds)
```

```{r table2}
knitr::kable(head(diamonds))
```

```{r table3}
DT::datatable(head(diamonds))
```


# Graphique Final
```{r histogram, message=FALSE, cache=FALSE}
possible <- names(diamonds)[sapply(diamonds, is.numeric)] #vecteur avec les noms de variables

selectInput(
  inputId = "selCol",
  label = "Select a column",
  choices = possible
)
renderPlot(ggplot(diamonds, aes_string(x=input$selCol)) +geom_histogram())
```
